LV2

### 2018-05-09 paper.tex
Language

@@

\section{Global analysis}
\label{sec:global-analysis}

@@

Client applications that produce tweets mostly from tracked accounts are used by the media. For the TweetDeck, TVNET Login, dlvr.it and SKATIES client applications the top 5 users are tracked media accounts that write dominantly in Latvian. The exceptions are a business account \sn{Kompresori} that was not tracked and tweets in three languages: Latvian, Russian and English, \sn{RusApollo} and \sn{TVNET\_rus} who tweet identical content exclusively in Russian, and \sn{SejasLV}, an exclusively Latvian account writing about celebrities that was not tracked.

@@

Some tweets come from social media networks. Facebook content mostly comes from tracked media accounts. The top 5 most active users are: \sn{mixnews\_lv}, the Russian edition of a media portal, \sn{Otkrito}, also the Russian edition of \sn{JaunsLV}, \sn{labdienlv}, \sn{ekonimikalv} and \sn{nozare}, all three belonging to one Latvian media portal. The fact that Russian accounts are not active among other clients might suggest that Russian content is not spread via Twitter, but, for example, via Facebook.

@@

>>>>

\usepackage{graphicx}

@@

\section{Twitter users}
\label{sec:global-analysis}

@@

Client applications that produce tweets mostly from tracked accounts are used by the media. For the TweetDeck, TVNET Login, dlvr.it and SKATIES client applications the top 5 users are tracked media accounts that write dominantly in Latvian. The exceptions are a business account \sn{Kompresori} that was not tracked and tweets in three languages: Latvian, Russian and English, \sn{RusApollo} and \sn{TVNET\_rus} who tweet identical content exclusively in Russian, and \sn{SejasLV}, an exclusively Latvian account writing about celebrities, which was not tracked.

@@

Some tweets come from social media networks. Facebook content mostly comes from tracked media accounts. The top 5 most active users are: \sn{mixnews\_lv}, the Russian edition of a media portal, \sn{Otkrito}, also the Russian edition of \sn{JaunsLV}, \sn{labdienlv}, \sn{ekonimikalv} and \sn{nozare}, all three belonging to one Latvian media portal. The fact that Russian accounts are not active among other clients might suggest that Russian content is not spread via Twitter, but via Facebook.

@@

\section{Language}
\label{sec:language}

Latvian is the dominant language: \hl{880\,351 (74\%)} tweets are written in it.\footnotemark{} There are \hl{12\,505 (11\%)} tweets in Russian, \hl{116203 (10\%)} in English and \hl{66\,969 (6\%)} in other languages. Figure~\ref{fig:rehydrated-tweets-count-by-day} shows the tweet volume over time.

Latvian dominates almost in every client application. Tweets coming from Foursquare are labeled as Latvian in \hl{78\%} cases (see Table~\ref{tab:source_counts}), that might be due to Latvian location names.

Russian tweets constitute of more then half tweets coming from TVNET, where its share is \hl{52\%} while Latvian is \hl{46.3\%}, and from Facebook, where the two most active users are Russian madia.

A lot of English content is coming form Instagram (\hl{32.9\%}), that might be due to the dominance of hashtags over other text. Also, there are many tweets labeled as written in other languages that come from Foursquare and Instagram. As Instagram posts are more likely to contain hashtags and Foursqure tweets contain location names, tweets should not be assigned a single language label, but instead be labeled as written in several languages.

\footnotetext{Twitter labels tweets with the language they are written in.}

\input{figures/rehydrated_tweets_count_by_day.tex}
